Supplemental Material for \\ Helixer: Cross-species Gene Annotation of Large Eucaryotic Genomes Using Deep Learning

### 2020-04-24 paper/supplements.tex
detailed plant performance added

\newpage
\section{Hyperparameters}

@@

\newpage
\section{Overlapping Evaluation by Species}
\label{sec:overlapping}
\begin{figure}[!h]
% \centerline{\includegraphics[height=0.01\paperheight]{images/overlapping/animals_overlapping}}
\caption{Caption, caption.}\label{fig:animals_overlapping}
\end{figure}

\newpage
\section{Training Data statistics}
\label{sec:training_data}
\begin{table}[!h]
\renewcommand\thetable{S1}
\centering
\begin{tabular}{@{}lll@{}}
\hline
& Animals & Plants\\ [0.5ex]
\hline
Average genome size in Gbp& 2.489 (+- 2.073) & 0.914 (+- 0.934) \\
Average gene length & 25,672 (+- 16,605) & 3,509 (+- 906)\\
Geenuff error rate & 0.253 (+- 0.138) & 0.134 (+- 0.072) \\
Fraction of class Intergenic & 0.752 (+- 0.05) & 0.808 (+- 0.106) \\
Fraction of class UTR & 0.013 (+- 0.011) & 0.033 (+- 0.023) \\
Fraction of class CDS & 0.028 (+- 0.028) & 0.077 (+- 0.052) \\
Fraction of class Intron  & 0.207 (+- 0.023) & 0.083 (+- 0.037) \\
\hline
\end{tabular}
\caption{The description of Table [?] applies here as well.}
\end{table}

>>>>

\newpage
\section{Model Evaluation by Species}
The following tables and plots show the prediction performance of Hexlixer for each species we worked with. The plots display the Subgenic F1 as well as the difference to AUGUSTUS with respect to the phylogenetic placement by NCBI Taxonomy.

\subsection{Animals}
\newpage

%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/animals_f1_scores_part1}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/animals_f1_scores_part2}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/animals_differences_part1}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/animals_differences_part2}}
%\end{figure}

\clearpage
\subsection{Plants}

\begin{table}[!h]
\resizebox{\textwidth}{!}{%
\renewcommand\thetable{S1}
\centering
%\vspace*{-3.5cm}
%\hspace*{-2.5cm}
\begin{tabular}{@{}llllllll@{}}
\hline
Genome & Acc Overall & IG F1 & UTR F1 & CDS F1 & Intron F1 & Subgenic F1& Genic F1 \\ [0.5ex]
\hline
Ananas\_comosus & 0.8749 & 0.9224 & 0.5674 & 0.8591 & 0.7325 & 0.7691 & 0.753 \\
Amaranthus\_hypochondriacus & 0.947 & 0.9728 & 0.5729 & 0.8535 & 0.8964 & 0.8856 & 0.864 \\
Arabidopsis\_lyrata & 0.9438 & 0.9701 & 0.637 & 0.8957 & 0.8196 & 0.8649 & 0.8314 \\
Asparagus\_officinalis & 0.6042 & 0.2635 & 0 & 0.8517 & 0.6979 & 0.7246 & 0.7206 \\
Arabidopsis\_thaliana & 0.9542 & 0.9729 & 0.7294 & 0.953 & 0.9329 & 0.9456 & 0.9181 \\
Amborella\_trichopoda & 0.6936 & 0.3451 & 0 & 0.8617 & 0.7816 & 0.7965 & 0.7933 \\
Brachypodium\_distachyon & 0.9326 & 0.9625 & 0.6232 & 0.9027 & 0.8772 & 0.8879 & 0.8426 \\
Brassica\_oleracea & 0.8648 & 0 & 0 & 0.9321 & 0.8785 & 0.911 & 0.9051 \\
Cicer\_arietinum & 0.8583 & 0.7838 & 0 & 0.8872 & 0.8952 & 0.8921 & 0.8885 \\
Citrus\_clementina & 0.9554 & 0.977 & 0.6277 & 0.9175 & 0.9027 & 0.9095 & 0.8771 \\
Capsella\_grandiflora & 0.9465 & 0.9656 & 0.7117 & 0.9545 & 0.9139 & 0.9389 & 0.9145 \\
Carica\_papaya & 0.9009 & 0.8926 & 0 & 0.9043 & 0.9156 & 0.9113 & 0.9057 \\
Chenopodium\_quinoa & 0.944 & 0.9703 & 0.6057 & 0.855 & 0.8311 & 0.8382 & 0.8244 \\
Chlamydomonas\_reinhardtii & 0.9484 & 0.9657 & 0.8039 & 0.9577 & 0.9546 & 0.9562 & 0.9254 \\
Capsella\_rubella & 0.9455 & 0.9669 & 0.668 & 0.9485 & 0.9138 & 0.9352 & 0.9032 \\
Cucumis\_sativus & 0.9515 & 0.9729 & 0.6174 & 0.9268 & 0.9237 & 0.9249 & 0.8962 \\
Citrus\_sinensis & 0.9545 & 0.9766 & 0.5878 & 0.9147 & 0.9027 & 0.9082 & 0.8778 \\
Coccomyxa\_subellipsoidea\_C-169 & 0.8467 & 0.8573 & 0.4164 & 0.8771 & 0.8896 & 0.8847 & 0.8409 \\
Chromochloris\_zofingiensis & 0.8849 & 0.3095 & 0 & 0.9129 & 0.9299 & 0.9203 & 0.9027 \\
Daucus\_carota & 0.8924 & 0.703 & 0 & 0.9284 & 0.9212 & 0.924 & 0.9175 \\
Dunaliella\_salina & 0.7458 & 0.8473 & 0.1832 & 0.6152 & 0.4306 & 0.4585 & 0.4352 \\
Eucalyptus\_grandis & 0.9447 & 0.9712 & 0.5327 & 0.8391 & 0.8245 & 0.8305 & 0.7956 \\
Eutrema\_salsugineum & 0.9555 & 0.9755 & 0.6501 & 0.9301 & 0.8985 & 0.9179 & 0.8908 \\
Fragaria\_vesca & 0.8776 & 0.9192 & 0.633 & 0.8666 & 0.7813 & 0.8218 & 0.7972 \\
Glycine\_max & 0.9755 & 0.9886 & 0.6564 & 0.9265 & 0.9165 & 0.92 & 0.8825 \\
Gossypium\_raimondii & 0.9784 & 0.9901 & 0.6836 & 0.9216 & 0.8835 & 0.9004 & 0.8701 \\
Helianthus\_annuus & 0.9747 & 0.9875 & 0.4514 & 0.7758 & 0.6562 & 0.6975 & 0.6763 \\
Hordeum\_vulgare & 0.9826 & 0.9917 & 0.4462 & 0.7774 & 0.624 & 0.6762 & 0.6503 \\
Kalanchoe\_fedtschenkoi & 0.9415 & 0.9693 & 0.6067 & 0.9112 & 0.8569 & 0.8833 & 0.8372 \\
Lactuca\_sativa & 0.98 & 0.9908 & 0.5771 & 0.867 & 0.7075 & 0.7848 & 0.7679 \\
Linum\_usitatissimum & 0.8411 & 0.3605 & 0 & 0.9452 & 0.8435 & 0.8991 & 0.8912 \\
Musa\_acuminata & 0.926 & 0.9598 & 0.4746 & 0.8856 & 0.8984 & 0.8946 & 0.8682 \\
Malus\_domestica & 0.9629 & 0.9816 & 0.6214 & 0.9049 & 0.8661 & 0.8825 & 0.852 \\
Manihot\_esculenta & 0.9748 & 0.9879 & 0.681 & 0.9365 & 0.9199 & 0.9261 & 0.8981 \\
Mimulus\_guttatus & 0.9704 & 0.985 & 0.7101 & 0.9405 & 0.9234 & 0.9319 & 0.9062 \\
Marchantia\_polymorpha & 0.9409 & 0.9708 & 0.6294 & 0.8786 & 0.8797 & 0.8792 & 0.8083 \\
Micromonas\_pusilla & 0.6896 & 0.639 & 0.3364 & 0.7517 & 0.617 & 0.7358 & 0.7223 \\
Micromonas\_sp.\_RCC299 & 0.592 & 0.5639 & 0.2706 & 0.637 & 0.5212 & 0.6301 & 0.6152 \\
Medicago\_truncatula & 0.9181 & 0.9474 & 0.6813 & 0.8625 & 0.8639 & 0.8633 & 0.8475 \\
Olea\_europaea & 0.7935 & 0.7695 & 0 & 0.794 & 0.8262 & 0.8142 & 0.8096 \\
Ostreococcus\_sp.\_lucimarinus & 0.2174 & 0.3241 & 0.0451 & 0.0746 & 0.0441 & 0.0734 & 0.0725 \\
Oryza\_sativa & 0.9061 & 0.9439 & 0.6234 & 0.8367 & 0.827 & 0.8312 & 0.8044 \\
Oropetium\_thomaeum & 0.8682 & 0.9194 & 0.5482 & 0.8605 & 0.8045 & 0.8275 & 0.8058 \\
Physcomitrella\_patens & 0.9589 & 0.9816 & 0.637 & 0.8701 & 0.8554 & 0.8626 & 0.8064 \\
Prunus\_persica & 0.9434 & 0.9688 & 0.6422 & 0.9089 & 0.8944 & 0.9012 & 0.8605 \\
Populus\_trichocarpa & 0.9609 & 0.9806 & 0.6771 & 0.9244 & 0.916 & 0.9196 & 0.882 \\
Porphyra\_umbilicalis & 0.7648 & 0.8529 & 0.2087 & 0.6096 & 0.2986 & 0.565 & 0.5139 \\
Ricinus\_communis & 0.9256 & 0.9442 & 0.4673 & 0.8984 & 0.9364 & 0.9192 & 0.9055 \\
Sorghum\_bicolor & 0.9654 & 0.983 & 0.5792 & 0.9033 & 0.8608 & 0.8775 & 0.8292 \\
Setaria\_italica & 0.9561 & 0.9775 & 0.6527 & 0.9166 & 0.8933 & 0.9037 & 0.8646 \\
Solanum\_lycopersicum & 0.9476 & 0.9725 & 0.4948 & 0.8826 & 0.8367 & 0.8509 & 0.8127 \\
Selaginella\_moellendorffii & 0.7166 & 0.7977 & 0.1825 & 0.7436 & 0.435 & 0.662 & 0.6388 \\
Spirodela\_polyrhiza & 0.7784 & 0 & 0 & 0.903 & 0.8414 & 0.8624 & 0.8529 \\
Solanum\_tuberosum & 0.7272 & 0.0994 & 0 & 0.8551 & 0.8199 & 0.8335 & 0.8299 \\
Triticum\_aestivum & 0.9238 & 0.9601 & 0.5238 & 0.8455 & 0.8356 & 0.8399 & 0.7961 \\
Theobroma\_cacao & 0.8743 & 0.9295 & 0.5257 & 0.8677 & 0.545 & 0.6421 & 0.627 \\
Volvox\_carteri & 0.8546 & 0.9045 & 0.5535 & 0.831 & 0.8241 & 0.8269 & 0.7706 \\
Vitis\_vinifera & 0.7918 & 0.0076 & 0 & 0.9229 & 0.8613 & 0.8771 & 0.8724 \\
Zostera\_marina & 0.9148 & 0.9463 & 0.5865 & 0.9052 & 0.8261 & 0.8571 & 0.8387 \\
Zea\_mays & 0.9843 & 0.9931 & 0.6073 & 0.886 & 0.854 & 0.8643 & 0.8406 \\
\hline
\end{tabular}}
\end{table}

\clearpage
\begin{figure}[!h]
\centerline{\includegraphics[width=1.0\textwidth]{images/plants_f1_scores}}
\end{figure}
\begin{figure}[!h]
\centerline{\includegraphics[width=1.0\textwidth]{images/plants_differences}}
\end{figure}

\clearpage
\section{Hyperparameters}

@@

\newpage
\section{Effect of Overlapping by Species}
\label{sec:overlapping}

The following plots show the effect of overlapping for each species we worked with individually. The plots are ordered with descending N75, as we found that overlapping tends to produce less desirable patterns in the prediction quality for the very fragmented genomes.

\subsection{Animals}
\newpage

%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals1}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals2}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals3}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals4}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals5}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals6}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals7}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals8}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals9}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals10}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals11}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals12}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_animals13}}
%\end{figure}
%
%\clearpage
%\subsection{Plants}
%
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_plants1}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_plants2}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_plants3}}
%\end{figure}
%\begin{figure}[!h]
%\centerline{\includegraphics[width=1.2\textwidth]{images/overlapping/montage_plants4}}
%\end{figure}
%
\clearpage
\section{Training Data statistics}
\label{sec:training_data}
\begin{table}[!h]
\renewcommand\thetable{S1}
\centering
\begin{tabular}{@{}lll@{}}
\hline
& Animals & Plants\\ [0.5ex]
\hline
Average genome size in Gbp& 2.489 (+- 2.073) & 0.914 (+- 0.934) \\
Average gene length & 25,672 (+- 16,605) & 3,509 (+- 906)\\
Geenuff error rate & 0.253 (+- 0.138) & 0.134 (+- 0.072) \\
Fraction of class Intergenic & 0.752 (+- 0.05) & 0.808 (+- 0.106) \\
Fraction of class UTR & 0.013 (+- 0.011) & 0.033 (+- 0.023) \\
Fraction of class CDS & 0.028 (+- 0.028) & 0.077 (+- 0.052) \\
Fraction of class Intron  & 0.207 (+- 0.023) & 0.083 (+- 0.037) \\
\hline
\end{tabular}
\caption{The description of Table [?] applies here as well.}
\end{table}
